How Optimal is Novel Word Recogntion Under Multimodal Uncertainty?

### 2019-04-11 Writeup/ms.tex
more revisions

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={How Optimal is Word-Referent Identification Under Multimodal Uncertainty?},
            pdfauthor={Abdellah Fourtassi~\& Michael C. Frank},
            pdfkeywords={Language understanding; audio-visual processing; word learning; speech
perception; computational modeling.},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{How Optimal is Word-Referent Identification Under Multimodal
Uncertainty?}
    \author{Abdellah Fourtassi\textsuperscript{1}~\& Michael C.
Frank\textsuperscript{1}}
    \date{}

@@

\abstract{
Identifying a spoken word in a referential context requires both the
ability to integrate multimodal input and the ability to reason under
uncertainty. How do these tasks interact with one another? We introduce
a paradigm that allows us to examine how adults identify words under
joint uncertainty in the auditory and visual modalities and propose an
ideal observer model of how cues in these modalities are combined
optimally. Model predictions are tested in three experiments where word
recognition is made under two kinds of uncertainty: category ambiguity
and perceptual noise. In all cases, the optimal model explains much of
the variance in human mean judgments. When the signal is not distorted
with noise, participants weight the auditory and visual cues optimally,
that is, according to the relative reliability of each modality. But
when one modality has noise added to it, human perceivers systematically
prefer the unperturbed modality to a greater extent than the optimal
model does. The study provides a formal framework which helps to
quantify how word form and word meaning interact in word recognition
under uncertainty. Moreover it offers a first step towards a model that
accounts for form-meaning synergies in early word learning.

@@

So far, we have only accounted for categorical variability. For
instance, if the speaker generates a target production \(a_t\) from an
auditory category \(p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A})\), the
ideal model assumes that it has direct access to this production token
(i.e., \(a=a_t\)), and that all uncertainty is about the category
membership of this token. However, we might also want to account for
internal noise in the brain and/or external noise in the environment.
For example, the observer might not have access to the exact produced
target, but only to the target perturbed by noise. If we assume this
noise to be normally distributed, that is,
\(p(a | a_t) \sim N(a_t, \sigma^2_{N_A})\), then integrating over
\(a_t\) leads to this new expression of the probability distribution:
\[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A}+\sigma^2_{N_A})\] Similarly, in
the case of sensory noise in the visual modality, we get:
\[ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{N_V})\] Finally,
using exactly the same derivation as above, we end up with the following
multimodal weighting scheme in the optimal combination model (Equation
1) which takes into account both categorical and sensory variability:

\[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
\[\beta_v \propto \frac{1}{\sigma^2_{V} +\sigma^2_{N_V}}.\]

@@

In this Experiment, we test the predictions of the model in the case
where uncertainty is due to categorical variability only (i.e.,
ambiguity in terms of category membership). We do not add any external
noise to the background and we assume that internal sensory noise is
negligible compared to categorical variability
(\(\sigma^2_{A} \gg \sigma^2_{N_A}\) and
\(\sigma^2_{V} \gg \sigma^2_{N_V}\)). Thus, we use the following cue
weighting scheme:

\[\beta_a \propto \frac{1}{\sigma^2_{A} + \sigma^2_{N_A}} \approx  \frac{1}{\sigma^2_{A} }\]
\[\beta_v \propto \frac{1}{\sigma^2_{V} + \sigma^2_{N_V}} \approx  \frac{1}{\sigma^2_{V} }.\]

@@

In this Experiment, we explored the effect of added noise on
performance. We tested a case where the background noise was added to
the auditory modality. We were interested to know if participants would
treat this new source of uncertainty as predicted by the optimal model,
that is, according to the following weighting scheme
\[\beta_a \propto \frac{1}{\sigma^2_{A}+\sigma^2_{N_A}}\]
\[\beta_v \propto \frac{1}{\sigma^2_{V}}.\] The alternative hypothesis
is that noise in one modality leads to a systematic preference for the
non-noisy modality.

@@

Similar to Experiment 2, we were interested to know if participants
would treat additional uncertainty as predicted by the optimal model,
that is, according to the following weighting scheme:
\[\beta_a \propto \frac{1}{\sigma^2_{A}}\]
\[\beta_v \propto \frac{1}{\sigma^2_{V}+\sigma^2_{N_V}}.\] The
alternative hypothesis is that noise in the visual modality would lead
to a preference for the auditory input, just like noise in the auditory
modality lead to a preference for the visual input in Experiment 2.

@@

\begin{figure}[htbp]
\centering
\includegraphics{ms_files/figure-latex/weights-1.pdf}
\caption{}
\end{figure}

@@

A planned sample of \(N =\) 100 participants was recruited online
through Amazon Mechanical Turk. We used the same exclusion criteria as
in both previous experiments. \(N =\) 2 participants were excluded
because they reported having a technical problem, and N=10 participants
were excluded because they had less than 50\% accurate responses on the
unambiguous training trials. The final sample consisted of \(N =\) 88
participants.

We recruited a planned sample of \(N=\) 50 participants from Amazon
Mechanical Turk. Only participants with US IP addresses and a task
approval rate above 99\% were allowed to participate. They were paid at
an hourly rate of \$6/hour. Participants were excluded if they reported
having experienced a technical problem of any sort during the online
experiment (\(N=\) 0 ), or if they had less than 75\% accurate responses
on the unambiguous training trials (\(N=\) 7). The final sample
consisted of \(N =\) 43 participants. All participants provided informed
consent before taking the
experiment.\footnote{The sample size, exclusion criteria and the main analysese were pre-registered at https://osf.io/h7mzp/.}

@@

The design and procedure were similar to Experiment 1. The only
difference was that we increased the number of responses elicited per
subject from 70 to 300.

@@

We analyzed cue combination at the individual level. For each
participant, we computed the optimal weighing,
\(\frac{\sigma^2_{A}}{\sigma^2_{V}}\), relative to the fitted (i.e.,
descriptive) weighing, \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}\). We show
the resulting distribution in Figure \ref{fig:weights}. We found that
the distribution centered around the optimal prediction (i.e., 1) with a
median value of 1.07 {[}\texttt{weight.median\_low},
\texttt{weight.median\_up}{]}.

{[}Here compare to random model to see whether the resuls were due to
measurement errors or to genuine betwee-subject variability, but isn't
that what the CI around the median show?{]}

@@

This experiment was an extension to Experiment 1. Through collecting
larger-size data per subject, we were able to analyze the cue
combination optim\&lity, not only at the population level, but also at
the individual level. The population-level analysis replicated the
results of Experiment 1. The individual-level analysis showed that the
distribution of cue combination scores had a unimodal shape
(approximating a normal distribution) centered around the optimal
combination. This finding rules out the hypotheis that optimality at the
population level (obtained in Experiment 1) is a spurious finding, i.e.,
only obtained via the aggregation of sub-otimal strategies. That said,
the large variance of this distribution indicates that some participants
tend to over-rely on the auditory modality and others tend to over-rely
on the visual modality (beyond measurement errors??).

@@

In all of our experiments, and when compared to the predictions of the
visual or the auditory models, participants generally relied on both
modalities to make their decisions in the bimodal condition. Indeed, in
Experiment 1 and 2, the optimal model accounted for more variance in
mean responses than the auditory or the visual models did. In Experiment
3, participants appeared to rely on one modality, but this was likely a
floor effect, due to the fact that noise made the visual input barely
perceptible. Further, in Experiment 1 and 4, which did not involve
background noise, participants not only relied on both modalities, but
generally weighted these modalities according to the predictions of the
optimal model, that is, according to their relative reliability. At the
individual level, however, we found evidence of a between-subject
variation: Some participants relied more on the visual modality, whereas
others relied more on the auditory modality.

Despite this overall pattern, we documented two major cases of
sub-optimality. First, in all experiments, the variance associated with
each modality increased in the bimodal condition compared to the
unimodal conditions. Participants responded slightly more randomly in
the bimodal condition than they did in the unimodal conditions. This
finding contrasts with research on multisensory integration where
associations tend to lead to a higher precision (e.g., Ernst \& Banks,
2002). Nevertheless, there is a crucial difference between these two
situations (besides the obvious difference in terms of the models used).
Research on multisensory integration (of which audio-visual speech is
arguably an instance) deals with redundant multimodal cues, and these
cues are integrated into a unified percept. In contrast, the
word-referent association is usually arbitrary and, in particular, the
cues are not expected to be correlated perceptually. Therefore the
observer cannot form a unified percept, rather, information must be
encoded separately from both modalities and must retain this encoding
through the decision making process. Retaining two separate cues at the
same time instead of forming one unified percept (as in multisensory
integration of redundant cues), or instead of retaining only one cue (as
in the unimodal case), is likely to place extra demands on cognitive
resources, which, in turn, could cause general performance to drop.
Indeed, there is evidence that cognitive load due to divided attention
(e.g., when performing two tasks at the same time) has a detrimental
effect on word recognition (Mattys \& Wiget, 2011).

@@

The second case of sub-optimality is related to how participants
weighted the cues from the visual and the auditory modalities in a noisy
context. In contrast to Experiment 1 where the combination was
indistinguishable from the optimal prediction, results of Experiment 2
and 3 suggested that participants had a systematic preference for the
other (non-noisy) modality. This finding aligns with previous work that
suggests that when speech signals are degraded, participants compensate
by relying more on other sources of information such as the accompanying
visual cues, the semantic/syntactic context, or the top-down
expectations. This kind of compensation has been observed with adults
(Mattys et al., 2012; Tanenhaus et al., 1995), and recent evidence
suggests that it starts in childhood (K. MacDonald, Marchman, Fernald,
\& Frank, 2018; Yurovsky, Case, \& Frank, 2017). Generally speaking,
previous experimental studies have not differentiated between an optimal
compensatory strategy (i.e., relying more on the alternative source
while using all information still available in the distorted signal),
and a sub-optimal strategy (i.e., relying more on the alternative source
while ignoring at least some of the information still available in the
distorted signal), however. The formal approach followed in this paper
allowed us to tease apart these two possibilities, and our analysis
supports the sub-optimal compensatory strategy: The preference for the
non-noisy modality is above and beyond what can be explained by the
relative reliability alone, meaning that the participants tend to ignore
at least part of the information still available in the noisy modality.

@@

An important question to ask is how the combination mechanism -- as
revealed in our controlled study -- scales up to real life situations.
Note that in order to test audio-visual cue combination under
uncertainty, we had to use a case of double ambiguity, that is, a case
where both the word forms (\enquote{ada}--\enquote{aba}) and the
referents (cat--dog) were similar and, thus, confusable. However, to
what extent does such a case occur in real languages? Cross-linguistic
corpus analyses suggest that lexical encoding tends, surprisingly,
towards double ambiguity in many languages (Dautriche, Mahowald, Gibson,
\& Piantadosi, 2017; Monaghan, Shillcock, Christiansen, \& Kirby, 2014;
Tamariz, 2008). For instance, Dautriche et al. (2017) analyzed 100
languages and found that words that are similar phonologically tend to
be similar semantically as well. These studies suggest that the case of
double uncertainty, though perhaps not pervasive, could be a real issue
in language as it increase the probability of confusability for many
words. That said, the inferences discussed here might play a more
significant role in naturalistic language comprehension when ambiguity
in both the form and/or the referent is induced by an \emph{external}
noisy context -- e.g., a very noisy party or a far away referent -- even
when these forms and referents are not confusable in normal situations.

@@

One salient limitation of our current work is that we used a restricted
and highly simplified stimulus set. For the auditory modality, we used
speech categories that varied along a single acoustic dimension. While
this dimension might be sufficient to recognize words in our specific
case, in general the speech signal is far more complex, varying along
several acoustic/phonetic dimensions. Additionally, these dimensions may
be highly variable due to various kinds of speaker and context
differences. The same thing can be said about our visual stimuli. Here
we used a continuum along a single morph dimension in order to construct
a multimodal input where the auditory and visual components have
symmetrical properties. Though such morph is not the exact visual
variability that people would encounter in their daily lives, it allowed
us to precisely test the role of auditory and visual information in the
cue combination process. Parameterizing semantic dimensions is a
notoriously difficult problem, but morphs have been used in previous
research as a reasonable proxy (Freedman et al., 2001; Havy \& Waxman,
2016; Sloutsky \& Fisher, 2004). It is an open question whether people
use the same strategy in controlled laboratory conditions and more
naturalistic settings where they have to deal with various levels of
variability. An answer to this question is likely to involve a
multifaceted research approach that goes beyond controlled
experimentation. We believe that one fruitful approach is to test
computational mechanisms with an input that more accurately represents
the full extent of multimodal variability in the learning environment
(Dupoux, 2018; Fourtassi, Schatz, Varadarajan, \& Dupoux, 2014; Harwath,
Torralba, \& Glass, 2016; B. C. Roy, Frank, DeCamp, \& Roy, 2015).

@@

Our work provides a formal framework where old and new questions about
word recognition in a referential context can be given a precise
formulation. While we focused on the case of arbitrary associations, it
is possible to use the same framework to study, for instance, the case
of \textit{iconicity}, that is, when there is a resemblance between the
sound of a word and its referent. Previous work has suggested that
iconicity, among other things, helps with learning (and generalizing the
meaning of) new words (see Dingemanse, Blasi, Lupyan, Christiansen, \&
Monaghan, 2015 for a review). Using the research strategy in this paper,
we can, for example, test whether iconicity has such an advantage
because it mitigates the sub-optimal patterns observed with more
arbitrary pairings. Finally, though the current framework only
characterizes adult word recognition, it provides a first step towards a
model where developmental questions can also be investigated. For
instance, future work should explore whether children, like adults, use
probabilistic cues from both the auditory and the visual input to
recognize ambiguous words, the extent to which they combine these cues
in an optimal fashion, and whether this cue combination help them to
refine their early phonological and semantic representations.

>>>>

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={How Optimal is Novel Word Recogntion Under Multimodal Uncertainty?},
            pdfauthor={Abdellah Fourtassi~\& Michael C. Frank},
            pdfkeywords={Language understanding; audio-visual processing; word learning; speech
perception; computational modeling.},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{How Optimal is Novel Word Recogntion Under Multimodal Uncertainty?}
    \author{Abdellah Fourtassi\textsuperscript{1}~\& Michael C.
Frank\textsuperscript{1}}
    \date{}

@@

\abstract{
Identifying a spoken word in a referential context requires both the
ability to integrate multimodal input and the ability to reason under
uncertainty. How do these tasks interact with one another? We introduce
a paradigm that allows us to examine how adults identify novel words
under joint uncertainty in the auditory and visual modalities and
propose an ideal observer model of how cues in these modalities are
combined optimally. Model predictions are tested in three experiments
where novel word recognition is made under two kinds of uncertainty:
category ambiguity and perceptual noise. In all cases, the optimal model
explains much of the variance in human mean judgments. When the signal
is not distorted with noise, participants weight the auditory and visual
cues optimally, that is, according to the relative reliability of each
modality. But when one modality has noise added to it, human perceivers
systematically prefer the unperturbed modality to a greater extent than
the optimal model does. The study provides a formal framework which
helps to quantify how word form and word meaning interact in word
recognition under uncertainty. Moreover it offers a first step towards a
model that accounts for form-meaning synergies in early word learning.

@@

So far, we have only accounted for categorical variability, i.e.,
\(\sigma^2_{A} = \sigma^2_{A_C}\). For instance, if the speaker
generates a target production \(a_t\) from an auditory category
\(p(a_t | A) \sim N(\mu_{A}, \sigma^2_{A_C})\), the ideal model assumes
that it has direct access to this production token (i.e., \(a=a_t\)),
and that all uncertainty is about the category membership of this token.
However, we might also want to account for internal noise in the brain
and/or external noise in the environment. For example, the observer
might not have access to the exact produced target, but only to the
target perturbed by noise. If we assume this noise to be normally
distributed, that is, \(p(a | a_t) \sim N(a_t, \sigma^2_{A_N})\), then
integrating over \(a_t\) leads to this new expression of the probability
distribution:
\[ p(a | A) \sim N(\mu_{A}, \sigma^2_{A_C}+\sigma^2_{A_N})\] Similarly,
in the case of sensory noise in the visual modality, we get:
\[ p(a | V) \sim N(\mu_{V}, \sigma^2_{V}+\sigma^2_{V_N})\] Finally,
using exactly the same derivation as above, we end up with the following
multimodal weighting scheme in the optimal combination model (Equation
1) which takes into account both categorical and sensory variability:

\[\beta_a \propto \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N}}\]
\[\beta_v \propto \frac{1}{\sigma^2_{V_C} +\sigma^2_{V_N}}.\]

@@

In this Experiment, we test the predictions of the model in the case
where uncertainty is due to categorical variability (i.e., ambiguity in
terms of category membership) and inherent sensory noise only. We do not
add any external noise to the background. Thus, we use the following cue
weighting scheme:

\[\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C} + \sigma^2_{A_N}}\]
\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C} + \sigma^2_{V_N}}.\]

@@

In this Experiment, we explored the effect of added envirnonmental noise
\(\sigma^2_{E}\) on performance. We tested a case where the background
noise was added to the auditory modality. We were interested to know if
participants would treat this new source of uncertainty as predicted by
the optimal model, that is, according to the following weighting scheme:

\[\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A} + \sigma^2_{E_A}}\]
\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{C_A}+\sigma^2_{N_A}}.\]

The alternative hypothesis is that noise in one modality leads to a
systematic preference for the non-noisy modality.

@@

Similar to Experiment 2, we were interested to know if participants
would treat additional uncertainty as predicted by the optimal model,
that is, according to the following weighting scheme:

\[\beta_a \propto \frac{1}{\sigma^2_{A}} = \frac{1}{\sigma^2_{A_C}+\sigma^2_{A_N}}\]
\[\beta_v \propto \frac{1}{\sigma^2_{V}} = \frac{1}{\sigma^2_{V_C}+\sigma^2_{V_N} + + \sigma^2_{V_E}}.\]

The alternative hypothesis is that noise in the visual modality would
lead to a preference for the auditory input, just like noise in the
auditory modality lead to a preference for the visual input in
Experiment 2.

@@

As we noted earlier, we did not have enough statistical power to fit a
different model for each participant. Thus, in the current experiment,
we re-ran Experiment 1 while extending its length, allowing us to
collect the number of datapoints necessary to fit the models for each
participant.

@@

We recruited a planned sample of \(N=\) 50 participants from Amazon
Mechanical Turk. Only participants with US IP addresses and a task
approval rate above 99\% were allowed to participate. They were paid at
an hourly rate of \$6/hour. Participants were excluded if they reported
having experienced a technical problem of any sort during the online
experiment (\(N=\) 0), or if they had less than 75\% accurate responses
on the unambiguous training trials (\(N=\) 7). The final sample
consisted of \(N =\) 43 participants. All participants provided informed
consent before taking the
experiment.\footnote{The sample size, exclusion criteria and the main analysese were pre-registered at https://osf.io/h7mzp/.}

@@

The design and procedure were similar to Experiment 1. There were,
however, two differences: 1) We increased the number of responses
elicited per subject from 70 to 300, and 2) we randomized the order of
the three blocks (i.e., visual-only, auditory-only, and audio-visual)
\emph{within} subject: Each participant saw the 3 blocks exactly 6
times, covering all possible ordering combinations. Unlike the
between-subjet randomzation in Experiment 1, this choices allowed us to
avoid any confounding effects due to the order of exposure.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/weights-1} \caption{The histogram shows the distribution of the participants' optimal cue weighing  relative the observed (i.e., descriptive) cue weigting (see Figure 3). Participant are optimal when this relative value is equal to 1 (red solid line). Values larger than 1 suggest over-reliance on the auditory modality whereas values lower than 1 suggest over-reliance on the visual modality. The density plot shows the distribution of simulated individual responses from the population-level probabilistic model. The dashed lines represent 95\% confidence intreval on this simulated distribution. Participants that are outside this interval can be understood as over-relying on the auditory or visual modality in a non-random way (i.e., with p < 0.05).}\label{fig:weights}
\end{figure}

@@

We analyzed the cue combination strategies at the individual level. For
each participant, we computed the optimal weighing,
\(\frac{\sigma^2_{A}}{\sigma^2_{V}}\), relative to the observed (i.e.,
descriptive) weighing, \(\frac{\sigma^2_{Ab}}{\sigma^2_{Vb}}\). We show
the resulting distribution in Figure \ref{fig:weights}. We note first
that the distribution has a rather bimodal shape, centered around the
optimal cue combination strategy. This finding rules out the hypotheis
that optimality at the population level is a spurious finding, i.e.,
only obtained via aggregating over various sub-otimal strategies.

In addition, we asked whether the observed variance in the individual
distribution was due to the randomness inherent to the process of
sampling from a probabilsitic model or whether it corresponded to a real
between-subject variability induced by different cue weighing
strategies. We simulated responses through sampling from the
population-level models and we computed the resuting distribution of cue
weighing for each simulated indivudual leading to the density function
in Figure \ref{fig:weights}. We can observe that most empirical values
fall within the 95\% confidence interval of the simulated density,
showing that this part of the variance can be due to mere sampling
randomness. However, a few participants had values outide this interval,
indicating that they systematically over-relied on the visual modality
(\(N=\) 5) or the auditory modality (\(N=\) 6) with p-value\$
\textless{} 0.05\$.

@@

This experiment was an extension to Experiment 1. Through collecting
larger-size data per subject, we were able to analyze the cue
combination optimality, not only at the population level, but also at
the individual level. The population-level analysis replicated the
results of Experiment 1. The individual-level analysis showed that the
distribution of cue combination scores had a unimodal shape centered
around the optimal combination, thus reflecting geuine cue combination
at the individual level. That said, the variance of this distribution
indicates that a few participants tended to over-rely on the auditory
modality and others tended to over-rely on the visual modality beyond
sampling errors.

@@

In all of our experiments, and when compared to the predictions of the
visual or the auditory models, participants generally relied on both
modalities to make their decisions in the bimodal condition. Indeed, in
Experiment 1 and 2, the optimal model accounted for more variance in
mean responses than the auditory or the visual models did. In Experiment
3, participants appeared to rely on one modality, but this was likely a
floor effect, due to the fact that noise made the visual input barely
perceptible. Further, in Experiment 1 and 4, which did not involve
background noise, participants not only relied on both modalities, but
generally weighted these modalities according to the predictions of the
optimal model, that is, according to their relative reliability. At the
individual level, Experiment 4 showed that most participant were
near-optimal. Only a few subjects over-relied on the auditory or visual
modalities beyond sampling errors.

More generally, the idea is that it is easier to integrate correlated,
redundant cues (e.g., the size of a an object based on both visual and
haptic information) into a unified percept, than it is to combine
perceptually uncorrelated cues to make a categorization judgement ,e.g.,
recognizing a freshly learned object category based on its distinctive
features such as shape and color. We argue that our task --- which
consists in combining perceptually uncorrelated cues from the auditory
and visual modalities to recognize a novel word --- is more similar to
the second case.

Despite this overall pattern, we documented two major cases of
sub-optimality. First, in all experiments, the variance associated with
each modality increased in the bimodal condition compared to the
unimodal conditions. Participants responded slightly more randomly in
the bimodal condition than they did in the unimodal conditions. This
finding contrasts with research on multisensory integration where
associations tend to lead to a higher precision (e.g., Ernst \& Banks,
2002). Nevertheless, research on multisensory integration has typically
dealt with a special case involving correlated, redundant multimodal
cues, e.g., determining the size of an object based on visual and haptic
information. Another possible case of multisensory integration involves
perceptually uncorrelated cues, e.g., recognizing a novel category based
on some features such as shape and color (e.g., Bankieris et al., 2017)
or, in our case, recognizing novel words cues based on phonological and
semantic cues. Perhaps it is harder to integrate uncorreated cues
because information form these cues must be encoded separately through
the decision making process. In fact, retaining two separate cues at the
same time instead of forming one unified percept (as in multisensory
integration of redundant cues), or instead of retaining only one cue (as
in the unimodal case), is likely to place extra demands on cognitive
resources, which, in turn, could cause general performance to drop.
Indeed, there is evidence that cognitive load due to divided attention
(e.g., when performing two tasks at the same time) has a detrimental
effect on word recognition (Mattys \& Wiget, 2011).

@@

The second case of sub-optimality is related to how participants
weighted the cues from the visual and the auditory modalities in a noisy
context. In contrast to Experiment 1 adn 4 where the combination was
indistinguishable from the optimal prediction, results of Experiment 2
and 3 suggested that participants had a systematic preference for the
other (non-noisy) modality. This finding aligns with previous work that
suggests that when the auditory signal is degraded, participants
compensate by relying more on other sources of information such as the
accompanying visual cues, the semantic/syntactic context, or the
top-down expectations. This kind of compensation has been observed with
adults (Mattys et al., 2012; Tanenhaus et al., 1995), and recent
evidence suggests that it starts in childhood (K. MacDonald, Marchman,
Fernald, \& Frank, 2018; Yurovsky, Case, \& Frank, 2017). Generally
speaking, previous experimental studies have not differentiated between
an optimal compensatory strategy (i.e., relying more on the alternative
source while using all information still available in the distorted
signal), and a sub-optimal strategy (i.e., relying more on the
alternative source while ignoring at least some of the information still
available in the distorted signal), however. The formal approach
followed in this paper allowed us to tease apart these two
possibilities, and our analysis supports the sub-optimal compensatory
strategy: The preference for the non-noisy modality is above and beyond
what can be explained by the relative reliability alone, meaning that
the participants tend to ignore at least part of the information still
available in the noisy modality.

@@

An important question to ask is how the combination mechanism --- as
revealed in our controlled study --- scales up to real life situations.
Note that in order to test audio-visual cue combination under
uncertainty, we had to use a case of double ambiguity, that is, a case
where both the word forms (\enquote{ada}--\enquote{aba}) and the
referents (cat--dog) were similar and, thus, confusable. However, to
what extent does such a case occur in real languages? Cross-linguistic
corpus analyses suggest that lexical encoding tends, surprisingly,
towards double ambiguity in many languages (Dautriche, Mahowald, Gibson,
\& Piantadosi, 2017; Monaghan, Shillcock, Christiansen, \& Kirby, 2014;
Tamariz, 2008). For instance, Dautriche et al. (2017) analyzed 100
languages and found that words that are similar phonologically tend to
be similar semantically as well. These studies suggest that the case of
double uncertainty, though perhaps not pervasive, could be a real issue
in language as it increase the probability of confusability for many
words. That said, the inferences discussed here might play a more
significant role in naturalistic language comprehension when ambiguity
in both the form and/or the referent is induced by an \emph{external}
noisy context --- e.g., a very noisy party or a far away referent ---
even when these forms and referents are not confusable in normal
situations.

@@

One salient limitation of our current work is that we used a restricted
and highly simplified stimulus set. For the auditory modality, we used
speech categories that varied along a single acoustic dimension. While
this dimension might be sufficient to recognize words in our specific
case, in general the speech signal is far more complex, varying along
several acoustic/phonetic dimensions. Additionally, these dimensions may
be highly variable due to various kinds of speaker and context
differences.

As for the visual modality, simulating meaningful variability is a more
difficult task. Indeed, parameterizing the semantic space has been a
notoriously hard problem and thus requires more simplifying assumptions.
Following previous studies (Freedman et al., 2001; Havy \& Waxman, 2016;
Sloutsky \& Fisher, 2004), we used a visual continuum along a
one-dimensional morph. This choice was motivated by the need to
construct a multimodal input where the auditory and visual components
are parametrized in a symmetrical fashion, allowing us to compare graded
effects of auditory and visual information on categorical judgment.
Though such a visual variability is clearly artificial (one does not
encounters in real life an animal that is, e.g., 30 \% dog and 70 \%
cat), we assume that the induced uncertainty form this visual stimuli
has a similar effect on word recognition as the uncertainty induced by
more naturalistic semantic variability.

It is an open question whether people use the same strategy in
controlled laboratory conditions and more naturalistic settings where
they have to deal with various levels of variability. An answer to this
question is likely to involve a multifaceted research approach that goes
beyond controlled experimentation. We believe that one fruitful approach
is to test computational mechanisms with an input that more accurately
represents the full extent of multimodal variability in the learning
environment (Dupoux, 2018; Fourtassi, Schatz, Varadarajan, \& Dupoux,
2014; Harwath, Torralba, \& Glass, 2016; B. C. Roy, Frank, DeCamp, \&
Roy, 2015).

@@

Our work provides a formal framework where old and new questions about
word recognition as well as other categorical tasks involving
uncorrelated cues can be given a precise formulation. We used a novel
method which enabled us not only to test for optimality as in prevous
studies (e.g., Bankieris et al., 2017; Bejjanki et al., 2011), but also
to examine systamtically how and by how much people deviate from
optimality in their combination strategies. This exploration is
important bla bla Rahnev and Denison (2018)

While we focused on the case of arbitrary associations in novel word
recognition, it is possible to use the same framework to study, for
instance, the case of \textit{iconicity}, that is, when there is a
resemblance between the sound of a word and its referent. Previous work
has suggested that iconicity, among other things, helps with learning
(and generalizing the meaning of) new words (see Dingemanse, Blasi,
Lupyan, Christiansen, \& Monaghan, 2015 for a review). Using the
research strategy in this paper, we can, for example, test whether
iconicity has such an advantage because it mitigates the sub-optimal
patterns observed with more arbitrary pairings.

Finally, though the current framework only characterizes adult word
recognition, it provides a first step towards a model where
developmental questions can also be investigated. For instance, future
work should explore whether children, like adults, use probabilistic
cues from both the auditory and the visual input to recognize ambiguous
words, the extent to which they combine these cues in an optimal
fashion, and whether this cue combination help them to refine their
early phonological and semantic representations.
